---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# ppl.fanf_tits

<!-- badges: start -->
<!-- badges: end -->

The `ppl.fanf_tits` project (and associated Github repository) is meant to contain all the R code I used to clean, explore, and analyse the data from the urban tits reproduction study launched in 2021 in the context of the PubPrivLands project. The aim was to investigate the importance of foraging habitat connectivity and patch size to explain the breeding success of urban Great tits (*Parus major*) and Blue tits (*Cyanistes caeruleus*) in Dijon, France.
In accordance to the FAIR (Findable, Accessible, Interoperable, Reusable) principles of open-science, you will find in the `ppl.fanf_tits` repository all the **data and codes** I used to produce the results presented in the manuscript we submitted to *Journal of Biogeography* and that is currently called "Foraging   habitat connectivity is more important than local habitat quantity to explain urban tits breeding success". Upon acceptance, I will update this file to link it to the DOI of the article (if you intend to reuse this dataset, please cite the associated article in your own communications).

If you have any question, feel free to contact me through my Github profile or using the e-mail address given in the manuscript.



## Content

In the `ppl.fanf_tits` repository, you will find several folders (and sub-folders):

* **data** -- contains the raw datasets used to produce the cleaned dataset (cf. ~/output/tables/ndata_final.csv) used for our formal statistical analyses. 
* **output** -- contains the elements produced by the R scripts, including the final dataset, some numeric results, tables and plots, as well as an **exploratory modelling report** (in .Rmd, .pdf or .html formats). The final dataset PDF metadata file will also be placed here upon acceptance of the article.
* **R** -- contains all R scripts. These are numbered. Files that start with 01_ contains the custom functions I made to wrangle, clean and prepare the data. Files that start with 02_ contains the code I used to analyses the data and produce the results reported and discussed in the manuscript. 
* **renv** -- contains the local library of the project. That is all the packages in the same version I used to produce the results (and as listed in the **renv.lock** file).



## Download and reproductibility

To download the `ppl.fanf_tits` repository, click on the green **Code** button on the top-right of the Github page (https://github.com/mrelnoob/ppl.fanf_tits) and select "Download ZIP". Once the repository is downloaded, you need to install the same global R version as the one I used (R 4.4.1.), set your working directory inside the repository, and run:

``` {r, eval = FALSE}
install.packages('renv')
renv::init()
renv::restore()
```

The `{renv}` package will read the **renv.lock** file and automatically install all the packages I used in the correct version (see also: https://rstudio.github.io/renv/). You may then run my R scripts. Note that many functions created in the R files are only used in the EDA report (RMarkdown file located within the "ouput/" folder).
