---
title: "Exploratory modelling report - Tits reproduction study, PubPrivLands project (Martin *et al.*, *in prep.*)"
author: "François-Marie Martin"
date: "`r format(Sys.time(), '%d %B, %Y')`"
bibliography: ppl.tits_biblio.bib
csl: fanf_style.csl
output: rmdformats::readthedown
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r data_import, warning=FALSE}
library(magrittr) # The only library that I truly need to load (in order to be able to use pipes).
.pardefault <- par()


### Loading the data ___________________________________________________________
ntits <- readr::read_csv2(here::here("output", "tables", "ndata_final.csv"), col_names = TRUE,
                          col_types = readr::cols(id_nestbox = readr::col_factor(),
                                                  id_patch = readr::col_factor(),
                                                  site = readr::col_factor(),
                                                  year = readr::col_factor(),
                                                  species = readr::col_factor(),
                                                  laying_date = readr::col_date(),
                                                  flight_date = readr::col_date(),
                                                  clutch_size = readr::col_integer(),
                                                  brood_size = readr::col_integer(),
                                                  fledgling_nb = readr::col_integer(),
                                                  manag_intensity = readr::col_factor(
                                                    ordered = TRUE,
                                                    levels = c("0", "1", "2"),
                                                    include_na = FALSE))) %>%
  dplyr::mutate(dplyr::across(where(is.matrix), as.numeric),
                dplyr::across(where(is.character), as.factor)) %>%
  dplyr::mutate(year = stats::relevel(x = year, ref = 3), # Assign 2019 as the reference group.
                species = stats::relevel(x = species, ref = 2)) %>% # Assign PM as the
  # reference group.
  dplyr::mutate(manag_low = ifelse(manag_intensity == "0", "1", "0"),
                manag_mid = ifelse(manag_intensity == "1", "1", "0"),
                manag_high = ifelse(manag_intensity == "2", "1", "0"))
# NOTE: I have to load the "tits" final dataset exported by 'tfinal_EDAta()' in order to avoid
# running the former function that is a bit long to run (but you can if you want).
ntits %>% dplyr::mutate(dplyr::across(where(is.character), as.factor)) -> ntits
```


# 1. Introduction
## 1.1. Regarding reproductibility

In order to facilitate any attempt at reproducing this study, here is a depiction of the system information used to prepare and analyse the data from the PubPrivLands tits reproduction study (Martin *et al.* , *in prep.*).

```{r session information}
rm(list=ls())
sessionInfo()
```

All codes and packages (through a {renv} project) used in this study can furthermore be found here: https://github.com/mrelnoob/ppl.fanf_tits 

\
\

## 1.2. What is this document about?

This report is meant to present all *exploratory modelling* that were conducted after our formal inferential modelling phase (cf. code and manuscript). These "exploratory models" were built in order to try and fine **tune some modelling components** (e.g. zero-inflation) or to **ascertain the robustness of our formal results** by using different proxies of our variables of interest: i.e. the *local patch area* and the *connectivity metric* (F metric: *log_F_metric_d2b1* in the R code).  
By nature, these models have far less support than the models used fro inference as the data have already been used for formal testing (thus type-I error rates aren't properly controlled for anymore)!
\
\

******

# 2. 

