---
title: "Exploratory modelling report - Tits reproduction study, PubPrivLands project (Martin *et al.*, *in prep.*)"
author: "François-Marie Martin"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  pdf_document:
    toc: yes
    toc_depth: '5'
  html_document:
    number_sections: yes
    toc: yes
    toc_depth: 5
---

```{r setup, echo=FALSE}
rm(list=ls())
knitr::opts_chunk$set(echo = FALSE)
```


```{r DATA_IMPORT, message=FALSE, warning=FALSE}
library(magrittr) # The only library that I truly need to load (in order to be able to use pipes).
.pardefault <- par()


### Loading the data ___________________________________________________________
ntits <- readr::read_csv2(here::here("output", "tables", "ndata_final.csv"), col_names = TRUE,
                          col_types = readr::cols(id_nestbox = readr::col_factor(),
                                                  id_patch = readr::col_factor(),
                                                  site = readr::col_factor(),
                                                  year = readr::col_factor(),
                                                  species = readr::col_factor(),
                                                  laying_date = readr::col_date(),
                                                  flight_date = readr::col_date(),
                                                  clutch_size = readr::col_integer(),
                                                  brood_size = readr::col_integer(),
                                                  fledgling_nb = readr::col_integer(),
                                                  manag_intensity = readr::col_factor(
                                                    ordered = TRUE,
                                                    levels = c("0", "1", "2"),
                                                    include_na = FALSE))) %>%
  dplyr::mutate(dplyr::across(where(is.matrix), as.numeric),
                dplyr::across(where(is.character), as.factor)) %>%
  dplyr::mutate(year = stats::relevel(x = year, ref = 3), # Assign 2019 as the reference group.
                species = stats::relevel(x = species, ref = 2)) %>% # Assign PM as the
  # reference group.
  dplyr::mutate(manag_low = ifelse(manag_intensity == "0", "1", "0"),
                manag_mid = ifelse(manag_intensity == "1", "1", "0"),
                manag_high = ifelse(manag_intensity == "2", "1", "0"),
                c.log_woody_vw = log_woody_vw - stats::median(log_woody_vw))
# NOTE: I have to load the "tits" final dataset exported by 'tfinal_EDAta()' in order to avoid
# running the former function that is a bit long to run (but you can if you want).
ntits %>% dplyr::mutate(dplyr::across(where(is.character), as.factor)) -> ntits
```


# 1. Introduction
## 1.1. Regarding reproductibility

In order to facilitate any attempt at reproducing this study, here is a depiction of the system information used to prepare and analyse the data from the PubPrivLands tits reproduction study (Martin *et al.* , *in prep.*).

```{r session information}
sessionInfo()
```

All codes and packages used in this study can furthermore be found here: https://github.com/mrelnoob/ppl.fanf_tits. All packages are availables with their correct version in the dedicated **{renv} project**.

\
\

## 1.2. What is this document about and how it it organised?

This report is meant to present all *exploratory modelling* that were conducted after our formal inferential modelling phase (cf. code and manuscript). These "exploratory models" were built in order to try and fine **tune some modelling components** (e.g. zero-inflation) or to **ascertain the robustness of our formal results** by using different proxies of our variables of interest: i.e. the *local patch area* and the *connectivity metric* (F metric: *log_F_metric_d2b1* in the R code).  
By nature, these models have far less support than the models used fro inference as the data have already been used for formal testing (thus type-I error rates aren't properly controlled for anymore)!

This report will be organised as follow:

1. We will first present the modelling results from all the variant models for **clutch size**, **nestling survival** and **mass**. Note that all models are simple variants of the final models we retained to formally test our two hypotheses.
2. Then, we will present the results from **nestling survival** models for which we tuned the *zero-inflation* (ZI) component to see if we could explain some of the excess of zeroes (that is total brood failures = 100% mortality rates).  

To keep things short, please note that we will not present models diagnostics (they were mostly good and they can easily be reproduced from our code) nor all possible combinations of models as we did not explored them all (we mostly focused on a few proxies).
\
\

******

# 2. Switched proxies models
## 2.1. Models to explain tits CLUTCH SIZE

```{r CS data preparation, warning=FALSE, message=FALSE, echo=FALSE}
## To remove probable outliers (see initial 'ttCy_comglmm1' diagnostics in the 03_01_ntits_inference_modelling R file):
ntits3 <- ntits[-c(111,156,170,181,210,227,326,362,374,379),]

## F+ COMPUTATION:
ntits3 %>% dplyr::mutate(Fplus = patch_area+F_metric_d2b1) %>%
  dplyr::mutate(log_Fplus = log10(Fplus)) -> ntits3
```



### 2.1.1. Using *woody_area* instead of *patch_area*

Results when we use the **total area of woody vegetation within 150 m of the nestboxes** (in m²) instead of the size of the **local patch area** (that is, the size of the patch of nesting/foraging habitat in which the nestbox is located) to explain the *size of tit clutches*:

```{r CS WOODY_AREA, warning=FALSE, message=FALSE, echo=FALSE}
## Fitting a regular Conway-Maxwell (COM) Poisson mixed model (GLMM):
ttCS_woodyAREA1 <- glmmTMB::glmmTMB(clutch_size ~ log_woody_area + log_F_metric_d2b1 + species +
                                    urban_intensity + manag_mid + manag_high +
                                    light_pollution + noise_m + traffic +
                                    cumdd_30 + laying_day + year + (1|id_nestbox),
                                 data = ntits3, family = glmmTMB::compois(link = "log"),
                                 dispformula = ~1) # Rather long to fit.

## Fitting the interaction model (COM-Poisson GLMM):
ttCS_woodyAREA2 <- glmmTMB::glmmTMB(clutch_size ~
                                    c.log_woody_area * c.log_F_metric_d2b1 + 
                                    species + urban_intensity + manag_mid + manag_high +
                                    light_pollution + noise_m + traffic +
                                    cumdd_30 + laying_day + year + (1|id_nestbox),
                                  data = ntits3, family = glmmTMB::compois(link = "log"),
                                  dispformula = ~1) # Rather long to fit.
summary(ttCS_woodyAREA1) # AIC = 1379.4 vs 1384 (for the final INFERENTIAL MODEL).
summary(ttCS_woodyAREA2) # AIC = 1379.3 vs 1386 (for the final INFERENTIAL MODEL), so the inclusion of the interaction doesn't help the model. Still, it is not far from being significant (sign of a more complex interaction?).
```



### 2.1.2. Using *woody_volume* instead of *patch_area*

Results when we use the **total volume of woody vegetation within 150 m of the nestboxes** (in m²) instead of the size of the **local patch area** (that is, the size of the patch of nesting/foraging habitat in which the nestbox is located) to explain the *size of tit clutches*:

```{r CS WOODY_VOLUME, warning=FALSE, message=FALSE, echo=FALSE}
## Fitting a regular Conway-Maxwell (COM) Poisson mixed model (GLMM):
ttCS_woodyVOL1 <- glmmTMB::glmmTMB(clutch_size ~ log_woody_vol + log_F_metric_d2b1 + species +
                                    urban_intensity + manag_mid + manag_high +
                                    light_pollution + noise_m + traffic +
                                    cumdd_30 + laying_day + year + (1|id_nestbox),
                                 data = ntits3, family = glmmTMB::compois(link = "log"),
                                 dispformula = ~1) # Rather long to fit.

## Fitting the interaction model (COM-Poisson GLMM):
ttCS_woodyVOL2 <- glmmTMB::glmmTMB(clutch_size ~
                                    c.log_woody_vol * c.log_F_metric_d2b1 + 
                                    species + urban_intensity + manag_mid + manag_high +
                                    light_pollution + noise_m + traffic +
                                    cumdd_30 + laying_day + year + (1|id_nestbox),
                                  data = ntits3, family = glmmTMB::compois(link = "log"),
                                  dispformula = ~1) # Rather long to fit.
summary(ttCS_woodyVOL1) # AIC = 1383.6 vs 1384 (for the final INFERENTIAL MODEL).
summary(ttCS_woodyVOL2) # AIC = 1383 vs 1386 (for the final INFERENTIAL MODEL), so the inclusion of the interaction doesn't help the model. Still, it is not far from being significant (sign of a more complex interaction?).
```



### 2.1.3. Using *woody_vw* instead of *patch_area*

Results when we use the **total volume of woody vegetation within 150 m of the nestboxes (weighted with a qualitative assessment of the structural complexity of the understory vegetation)** instead of the size of the **local patch area** (that is, the size of the patch of nesting/foraging habitat in which the nestbox is located) to explain the *size of tit clutches*:

```{r CS WOODY_VW, warning=FALSE, message=FALSE, echo=FALSE}
## Fitting a regular Conway-Maxwell (COM) Poisson mixed model (GLMM):
ttCS_woodyVW1 <- glmmTMB::glmmTMB(clutch_size ~ log_woody_vw + log_F_metric_d2b1 + species +
                                    urban_intensity + manag_mid + manag_high +
                                    light_pollution + noise_m + traffic +
                                    cumdd_30 + laying_day + year + (1|id_nestbox),
                                 data = ntits3, family = glmmTMB::compois(link = "log"),
                                 dispformula = ~1) # Rather long to fit.

## Fitting the interaction model (COM-Poisson GLMM):
ttCS_woodyVW2 <- glmmTMB::glmmTMB(clutch_size ~
                                    c.log_woody_vol * c.log_F_metric_d2b1 + 
                                    species + urban_intensity + manag_mid + manag_high +
                                    light_pollution + noise_m + traffic +
                                    cumdd_30 + laying_day + year + (1|id_nestbox),
                                  data = ntits3, family = glmmTMB::compois(link = "log"),
                                  dispformula = ~1) # Rather long to fit.
summary(ttCS_woodyVW1) # AIC = 1383.8 vs 1384 (for the final INFERENTIAL MODEL).
summary(ttCS_woodyVW2) # AIC = 1383 vs 1386 (for the final INFERENTIAL MODEL). Here again, the interaction is not that far from being significant.
```



### 2.1.4. Using *Fplus* instead of *patch_area*

Results when we use the *F_plus* variable, i.e. the **addition** of the **local patch area** and the **F-metric** to explain the *size of tit clutches*:

```{r CS Fplus, warning=FALSE, message=FALSE, echo=FALSE}
## Fitting a regular Conway-Maxwell (COM) Poisson mixed model (GLMM):
ttCS_Fplus1 <- glmmTMB::glmmTMB(clutch_size ~ log_Fplus + species +
                                    urban_intensity + manag_mid + manag_high +
                                    light_pollution + noise_m + traffic +
                                    cumdd_30 + laying_day + year + (1|id_nestbox),
                                 data = ntits3, family = glmmTMB::compois(link = "log"),
                                 dispformula = ~1) # Rather long to fit.
summary(ttCS_Fplus1) # AIC = 1391.3 vs 1384 (for the final INFERENTIAL MODEL).
```



### 2.1.5. Using *F_metric_d2b0* instead of *F_metric_d2b1*

Results when we use the *F_metric_d2b0* variable, i.e. the *F-metric* with no weighting for the size of the patches, to explain the *size of tit clutches*:

```{r CS Fd2b0, warning=FALSE, message=FALSE, echo=FALSE}
## Fitting a regular Conway-Maxwell (COM) Poisson mixed model (GLMM):
ttCS_Fmod1 <- glmmTMB::glmmTMB(clutch_size ~ log_patch_area + log_F_metric_d2b0 + species +
                                    urban_intensity + manag_mid + manag_high +
                                    light_pollution + noise_m + traffic +
                                    cumdd_30 + laying_day + year + (1|id_nestbox),
                                  data = ntits3, family = glmmTMB::compois(link = "log"),
                                  dispformula = ~1) # Rather long to fit.

## Fitting the interaction model (COM-Poisson GLMM):
ttCS_Fmod2 <- glmmTMB::glmmTMB(clutch_size ~
                                    c.log_patch_area * log_F_metric_d2b0 + species +
                                    urban_intensity + manag_mid + manag_high +
                                    light_pollution + noise_m + traffic +
                                    cumdd_30 + laying_day + year + (1|id_nestbox),
                                  data = ntits3, family = glmmTMB::compois(link = "log"),
                                  dispformula = ~1) # Rather long to fit.
summary(ttCS_Fmod1) # AIC = 1384 vs 1384 (for the final INFERENTIAL MODEL).
summary(ttCS_Fmod2) # AIC = 1385.4 vs 1384 (for the final INFERENTIAL MODEL).
```

\
\

******

## 2.2. Models to explain tits NESTLING SURVIVAL

```{r FS data preparation, warning=FALSE, message=FALSE, echo=FALSE}
ntits3 <- ntits[-c(which(ntits$brood_size == 0)),]

##  F+ COMPUTATION:
ntits3 %>% dplyr::mutate(Fplus = patch_area+F_metric_d2b1) %>%
  dplyr::mutate(log_Fplus = log10(Fplus)) -> ntits3
```



### 2.2.1. Using *woody_area* instead of *patch_area*


Results when we use the **total area of woody vegetation within 150 m of the nestboxes** (in m²) instead of the size of the **local patch area** (that is, the size of the patch of nesting/foraging habitat in which the nestbox is located) to explain the *survival of tits nestlings*:

```{r FS WOODY_AREA, warning=FALSE, message=FALSE, echo=FALSE}
## Fitting a ZIBBIN GLMM:
ttFS_woodyAREA1 <- glmmTMB::glmmTMB(fledgling_nb/brood_size ~ log_woody_area + log_F_metric_d2b1 +
                                        clutch_size +
                                        urban_intensity + manag_mid + manag_high +
                                        light_pollution + noise_m + traffic +
                                        min_t_between + laying_day + year + (1|id_nestbox),
                                      weights = brood_size, data = ntits3,
                                      family = glmmTMB::betabinomial(link = "logit"),
                                      ziformula = ~1) # Intercept only.

## Fitting the interaction model (COM-Poisson GLMM):
ttFS_woodyAREA2 <- glmmTMB::glmmTMB(fledgling_nb/brood_size ~
                                    c.log_woody_area * c.log_F_metric_d2b1 +
                                        clutch_size +
                                        urban_intensity + manag_mid + manag_high +
                                        light_pollution + noise_m + traffic +
                                        min_t_between + laying_day + year + (1|id_nestbox),
                                      weights = brood_size, data = ntits3,
                                      family = glmmTMB::betabinomial(link = "logit"),
                                      ziformula = ~1) # Rather long to fit.
summary(ttFS_woodyAREA1) # AIC = 1379.6 vs 1379.5 (for the final INFERENTIAL MODEL).
summary(ttFS_woodyAREA2) # AIC = 1378.2 vs 1376.5 (for the final INFERENTIAL MODEL). Note that the interaction is almost significant.
```



### 2.2.2. Using *woody_volume* instead of *patch_area*


Results when we use the **total volume of woody vegetation within 150 m of the nestboxes** (in m²) instead of the size of the **local patch area** (that is, the size of the patch of nesting/foraging habitat in which the nestbox is located) to explain the *survival of tits nestlings*:

```{r FS WOODY_VOLUME, warning=FALSE, message=FALSE, echo=FALSE}
## Fitting a ZIBBIN GLMM:
ttFS_woodyVOL1 <- glmmTMB::glmmTMB(fledgling_nb/brood_size ~ log_woody_vol + log_F_metric_d2b1 +
                                        clutch_size +
                                        urban_intensity + manag_mid + manag_high +
                                        light_pollution + noise_m + traffic +
                                        min_t_between + laying_day + year + (1|id_nestbox),
                                      weights = brood_size, data = ntits3,
                                      family = glmmTMB::betabinomial(link = "logit"),
                                      ziformula = ~1) # Intercept only.

## Fitting the interaction model (COM-Poisson GLMM):
ttFS_woodyVOL2 <- glmmTMB::glmmTMB(fledgling_nb/brood_size ~
                                    c.log_woody_vol * c.log_F_metric_d2b1 +
                                        clutch_size +
                                        urban_intensity + manag_mid + manag_high +
                                        light_pollution + noise_m + traffic +
                                        min_t_between + laying_day + year + (1|id_nestbox),
                                      weights = brood_size, data = ntits3,
                                      family = glmmTMB::betabinomial(link = "logit"),
                                      ziformula = ~1) # Rather long to fit.
summary(ttFS_woodyVOL1) # AIC = 1379.4 vs 1379.5 (for the final INFERENTIAL MODEL).
summary(ttFS_woodyVOL2) # AIC = 1376.7 vs 1376.5 (for the final INFERENTIAL MODEL). Note that the interaction is almost significant.
```



### 2.2.3. Using *woody_vw* instead of *patch_area*

Results when we use the **total volume of woody vegetation within 150 m of the nestboxes (weighted with a qualitative assessment of the structural complexity of the understory vegetation)** instead of the size of the **local patch area** (that is, the size of the patch of nesting/foraging habitat in which the nestbox is located) to explain the *survival of tits nestlings*:

```{r FS WOODY_VW, warning=FALSE, message=FALSE, echo=FALSE}
## Fitting a ZIBBIN GLMM:
ttFS_woodyVW1 <- glmmTMB::glmmTMB(fledgling_nb/brood_size ~ log_woody_vw + log_F_metric_d2b1 +
                                        clutch_size +
                                        urban_intensity + manag_mid + manag_high +
                                        light_pollution + noise_m + traffic +
                                        min_t_between + laying_day + year + (1|id_nestbox),
                                      weights = brood_size, data = ntits3,
                                      family = glmmTMB::betabinomial(link = "logit"),
                                      ziformula = ~1) # Intercept only.

## Fitting the interaction model (COM-Poisson GLMM):
ttFS_woodyVW2 <- glmmTMB::glmmTMB(fledgling_nb/brood_size ~
                                    c.log_woody_vw * c.log_F_metric_d2b1 +
                                        clutch_size +
                                        urban_intensity + manag_mid + manag_high +
                                        light_pollution + noise_m + traffic +
                                        min_t_between + laying_day + year + (1|id_nestbox),
                                      weights = brood_size, data = ntits3,
                                      family = glmmTMB::betabinomial(link = "logit"),
                                      ziformula = ~1) # Rather long to fit.
summary(ttFS_woodyVW1) # AIC = 1379.6 vs 1379.5 (for the final INFERENTIAL MODEL).
summary(ttFS_woodyVW2) # AIC = 1376.7 vs 1376.5 (for the final INFERENTIAL MODEL). Note that the interaction is almost significant.
```

### 2.2.4. Using *Fplus* instead of *patch_area*


Results when we use the *F_plus* variable, i.e. the **addition** of the **local patch area** and the **F-metric** to explain the *survival of tits nestlings*:

```{r FS Fplus, warning=FALSE, message=FALSE, echo=FALSE}
## Fitting a ZIBBIN GLMM:
ttFS_Fplus1 <- glmmTMB::glmmTMB(fledgling_nb/brood_size ~ log_Fplus +
                                        clutch_size +
                                        urban_intensity + manag_mid + manag_high +
                                        light_pollution + noise_m + traffic +
                                        min_t_between + laying_day + year + (1|id_nestbox),
                                      weights = brood_size, data = ntits3,
                                      family = glmmTMB::betabinomial(link = "logit"),
                                      ziformula = ~1) # Intercept only.

summary(ttFS_Fplus1) # AIC = 1377.6 vs 1379.5 (for the final INFERENTIAL MODEL).
```



### 2.2.5. Using *F_metric_d2b0* instead of *F_metric_d2b1*

Results when we use the *F_metric_d2b0* variable, i.e. the *F-metric* with no weighting for the size of the patches, to explain the *nestling survival*:

```{r FS Fd2b0, warning=FALSE, message=FALSE, echo=FALSE}
## Fitting a ZIBBIN GLMM:
ttFS_Fmod1 <- glmmTMB::glmmTMB(fledgling_nb/brood_size ~ log_woody_vol + log_F_metric_d2b0 +
                                        clutch_size +
                                        urban_intensity + manag_mid + manag_high +
                                        light_pollution + noise_m + traffic +
                                        min_t_between + laying_day + year + (1|id_nestbox),
                                      weights = brood_size, data = ntits3,
                                      family = glmmTMB::betabinomial(link = "logit"),
                                      ziformula = ~1) # Intercept only.

ttFS_Fmod2 <- glmmTMB::glmmTMB(fledgling_nb/brood_size ~
                                    c.log_woody_vol * c.log_F_metric_d2b0 +
                                        clutch_size +
                                        urban_intensity + manag_mid + manag_high +
                                        light_pollution + noise_m + traffic +
                                        min_t_between + laying_day + year + (1|id_nestbox),
                                      weights = brood_size, data = ntits3,
                                      family = glmmTMB::betabinomial(link = "logit"),
                                      ziformula = ~1) # Rather long to fit.
summary(ttFS_Fmod1) # AIC = 1381.4 vs 1379.5 (for the final INFERENTIAL MODEL).
summary(ttFS_Fmod2) # AIC = 1373 vs 1376.5 (for the final INFERENTIAL MODEL). Note that the interaction is significant and the AIC is quite improved!
```

\
\

******

## 2.3. Models to explain tits NESTLING MASS

```{r MA data preparation, warning=FALSE, message=FALSE, echo=FALSE}
ntits %>% dplyr::filter(is.na(mass) == FALSE) -> ntits3

##  F+ COMPUTATION:
ntits3 %>% dplyr::mutate(Fplus = patch_area+F_metric_d2b1) %>%
  dplyr::mutate(log_Fplus = log10(Fplus)) -> ntits3
```



### 2.3.1. Using *woody_area* instead of *patch_area*


Results when we use the **total area of woody vegetation within 150 m of the nestboxes** (in m²) instead of the size of the **local patch area** (that is, the size of the patch of nesting/foraging habitat in which the nestbox is located) to explain the *mass of tits nestlings*:

```{r MA WOODY_AREA, warning=FALSE, message=FALSE, echo=FALSE}
ttMA_woodyAREA1 <- glmmTMB::glmmTMB(mass ~ log_woody_area + log_F_metric_d2b1 + 
                                      species + clutch_size +
                                urban_intensity + manag_mid + manag_high +
                                light_pollution + noise_m + traffic +
                                min_t_between + laying_day + year + (1|id_nestbox),
                              data = ntits3, family = "gaussian")

ttMA_woodyAREA2 <- glmmTMB::glmmTMB(mass ~ c.log_woody_area * c.log_F_metric_d2b1 + species +
                                clutch_size + urban_intensity + manag_mid + manag_high +
                                light_pollution + noise_m + traffic +
                                min_t_between + laying_day + year + (1|id_nestbox),
                              data = ntits3, family = "gaussian")
summary(ttMA_woodyAREA1) # AIC = 1142.8 vs 1143.3. (for the final INFERENTIAL MODEL).
summary(ttMA_woodyAREA2) # AIC = 1144.2 vs 1144.7 (for the final INFERENTIAL MODEL).
```



### 2.3.2. Using *woody_volume* instead of *patch_area*

Results when we use the **total volume of woody vegetation within 150 m of the nestboxes** (in m²) instead of the size of the **local patch area** (that is, the size of the patch of nesting/foraging habitat in which the nestbox is located) to explain the *mass of tits nestlings*:

```{r MA WOODY_VOLUME, warning=FALSE, message=FALSE, echo=FALSE}
ttMA_woodyVOL1 <- glmmTMB::glmmTMB(mass ~ log_woody_vol + log_F_metric_d2b1 + 
                                      species + clutch_size +
                                urban_intensity + manag_mid + manag_high +
                                light_pollution + noise_m + traffic +
                                min_t_between + laying_day + year + (1|id_nestbox),
                              data = ntits3, family = "gaussian")

ttMA_woodyVOL2 <- glmmTMB::glmmTMB(mass ~ c.log_woody_vol * c.log_F_metric_d2b1 + species +
                                clutch_size + urban_intensity + manag_mid + manag_high +
                                light_pollution + noise_m + traffic +
                                min_t_between + laying_day + year + (1|id_nestbox),
                              data = ntits3, family = "gaussian")
summary(ttMA_woodyVOL1) # AIC = 1142.5 vs 1143.3. (for the final INFERENTIAL MODEL).
summary(ttMA_woodyVOL2) # AIC = 1144.3 vs 1144.7 (for the final INFERENTIAL MODEL).
```



### 2.3.3. Using *woody_vw* instead of *patch_area*

Results when we use the **total volume of woody vegetation within 150 m of the nestboxes (weighted with a qualitative assessment of the structural complexity of the understory vegetation)** instead of the size of the **local patch area** (that is, the size of the patch of nesting/foraging habitat in which the nestbox is located) to explain the *mass of tits nestlings*:

```{r MA WOODY_VW, warning=FALSE, message=FALSE, echo=FALSE}
ttMA_woodyVW1 <- glmmTMB::glmmTMB(mass ~ log_woody_vw + log_F_metric_d2b1 + 
                                      species + clutch_size +
                                urban_intensity + manag_mid + manag_high +
                                light_pollution + noise_m + traffic +
                                min_t_between + laying_day + year + (1|id_nestbox),
                              data = ntits3, family = "gaussian")

ttMA_woodyVW2 <- glmmTMB::glmmTMB(mass ~ c.log_woody_vw * c.log_F_metric_d2b1 + species +
                                clutch_size + urban_intensity + manag_mid + manag_high +
                                light_pollution + noise_m + traffic +
                                min_t_between + laying_day + year + (1|id_nestbox),
                              data = ntits3, family = "gaussian")
summary(ttMA_woodyVW1) # AIC = 1143 vs 1143.3. (for the final INFERENTIAL MODEL).
summary(ttMA_woodyVW2) # AIC = 1144.9 vs 1144.7 (for the final INFERENTIAL MODEL).
```

### 2.3.4. Using *Fplus* instead of *patch_area*

Results when we use the *F_plus* variable, i.e. the **addition** of the **local patch area** and the **F-metric** to explain the *mass of tits nestlings*:

```{r MA Fplus, warning=FALSE, message=FALSE, echo=FALSE}
ttMA_Fplus <- glmmTMB::glmmTMB(mass ~ log_Fplus + species + clutch_size +
                                urban_intensity + manag_mid + manag_high +
                                light_pollution + noise_m + traffic +
                                min_t_between + laying_day + year + (1|id_nestbox),
                              data = ntits3, family = "gaussian")
summary(ttMA_Fplus) # AIC = 1142.3 vs 1143.3. (for the final INFERENTIAL MODEL).
```



### 2.3.5. Using *F_metric_d2b0* instead of *F_metric_d2b1*

Results when we use the *F_metric_d2b0* variable, i.e. the *F-metric* with no weighting for the size of the patches, to explain the *nestling mass*:

```{r MA Fd2b0, warning=FALSE, message=FALSE, echo=FALSE}
ttMA_Fmod1 <- glmmTMB::glmmTMB(mass ~ log_woody_vol + log_F_metric_d2b0 + 
                                      species + clutch_size +
                                urban_intensity + manag_mid + manag_high +
                                light_pollution + noise_m + traffic +
                                min_t_between + laying_day + year + (1|id_nestbox),
                              data = ntits3, family = "gaussian")

ttMA_Fmod2 <- glmmTMB::glmmTMB(mass ~ c.log_woody_vol * c.log_F_metric_d2b0 + species +
                                clutch_size + urban_intensity + manag_mid + manag_high +
                                light_pollution + noise_m + traffic +
                                min_t_between + laying_day + year + (1|id_nestbox),
                              data = ntits3, family = "gaussian")
summary(ttMA_Fmod1) # AIC = 1141.6 vs 1143.3. (for the final INFERENTIAL MODEL).
summary(ttMA_Fmod2) # AIC = 1143.6 vs 1144.7 (for the final INFERENTIAL MODEL).
```

\
\

******

## 2.4. Conclusion on switched proxies models

The variant models results presented in the above sections give **pretty similar *patterns of results* ** to our final inferential models, regardless of the reproductive trait investigated. Interestingly:

* The model using *woody_area* gives slightly better results than our *inferential model* to explain **clutch size**, with the *F-metric* having a significant positive effect on tits clutch size. It could be a sign of the existence of a more complex interaction to be determined. 
* Estimates, standard errors and their associated p-values jitter a bit, which is to be expected. Some parameterisations even gave "better" results (as in lower p-values, which is what many scientist run after), but that is not the point.
* Overall, results remain consistent, particularly the fact that *connectivity metrics* seem to have a positive effect on reproductive traits, whereas the *amount of local habitat* alone (e.g. patch area, woody vegetation area or volume) is not a good predictor of the traits examined here, at least not with our dataset. It should be noted that we also ran the same models but with predictors computed using other buffer radiuses, and patterns remained the same. We do not present them here for the sake of conciseness (but you can easily reproduce these results using the R files), this report is already long enough (especially for a report that nobody will ever read...).

\
\

******

# 3. Tuning the zero-inflation (ZI) component of the NESTLING SURVIVAL model
## 3.1. Exploratory models

```{r ZI tuning, warning=FALSE, message=FALSE, echo=FALSE}
ntits3 <- ntits[-c(which(ntits$brood_size == 0)),]



## Tuning the ZI part of the model:
ttFS_zibbin_glm1e <- glmmTMB::glmmTMB(fledgling_nb/brood_size ~ log_patch_area + log_F_metric_d2b1 +
                                        clutch_size +
                                        urban_intensity + manag_mid + manag_high +
                                        light_pollution + noise_m + traffic +
                                        min_t_between + laying_day + year,
                                      weights = brood_size, data = ntits3,
                                      family = glmmTMB::betabinomial(link = "logit"),
                                      ziformula = ~min_t_between) # Intercept only.

ttFS_zibbin_glm1f <- glmmTMB::glmmTMB(fledgling_nb/brood_size ~ log_patch_area + log_F_metric_d2b1 +
                                        clutch_size +
                                        urban_intensity + manag_mid + manag_high +
                                        light_pollution + noise_m + traffic +
                                        min_t_between + laying_day + year,
                                      weights = brood_size, data = ntits3,
                                      family = glmmTMB::betabinomial(link = "logit"),
                                      ziformula = ~log_F_metric_d2b1) # Intercept only.

ttFS_zibbin_glm1g <- glmmTMB::glmmTMB(fledgling_nb/brood_size ~ log_patch_area + log_F_metric_d2b1 +
                                        clutch_size +
                                        urban_intensity + manag_mid + manag_high +
                                        light_pollution + noise_m + traffic +
                                        min_t_between + laying_day + year,
                                      weights = brood_size, data = ntits3,
                                      family = glmmTMB::betabinomial(link = "logit"),
                                      ziformula = ~log_patch_area) # Intercept only.

ttFS_zibbin_glm1h <- glmmTMB::glmmTMB(fledgling_nb/brood_size ~ log_patch_area + log_F_metric_d2b1 +
                                        clutch_size +
                                        urban_intensity + manag_mid + manag_high +
                                        light_pollution + noise_m + traffic +
                                        min_t_between + laying_day + year,
                                      weights = brood_size, data = ntits3,
                                      family = glmmTMB::betabinomial(link = "logit"),
                                      ziformula = ~min_t_between+urban_intensity+year) # Intercept only.

ttFS_zibbin_glmm1h <- glmmTMB::glmmTMB(fledgling_nb/brood_size ~ log_patch_area + log_F_metric_d2b1 +
                                        clutch_size +
                                        urban_intensity + manag_mid + manag_high +
                                        light_pollution + noise_m + traffic +
                                        min_t_between + laying_day + year + (1|id_nestbox),
                                      weights = brood_size, data = ntits3,
                                      family = glmmTMB::betabinomial(link = "logit"),
                                      ziformula = ~min_t_between+urban_intensity+year) # Intercept only.

ttFS_zibbin_glm1i <- glmmTMB::glmmTMB(fledgling_nb/brood_size ~ log_patch_area + log_F_metric_d2b1 +
                                        clutch_size +
                                        urban_intensity + manag_mid + manag_high +
                                        light_pollution + noise_m + traffic +
                                        min_t_between + laying_day + year,
                                      weights = brood_size, data = ntits3,
                                      family = glmmTMB::betabinomial(link = "logit"),
                                      ziformula = ~laying_day+urban_intensity+year) # Intercept only.
summary(ttFS_zibbin_glm1e) # AIC = 1374.7 vs 1377.5 (for the final INFERENTIAL MODEL [GLM]).
summary(ttFS_zibbin_glm1f) # AIC = 1375.2.
summary(ttFS_zibbin_glm1g) # AIC = 1376.8.
summary(ttFS_zibbin_glm1h) # AIC = 1364.9.
summary(ttFS_zibbin_glmm1h) # AIC = 1366.9 (mind the RE's uselessness).
summary(ttFS_zibbin_glm1i) # AIC = 1367.1.
# I also tried removing "traffic" and it doesn't change things much. When we use the "F-metric" along 
# with "urban_intensity" to model the ZI-part of the model, the effect of the "F-metric" utterly 
# disappear suggesting that connectivity does not influence total fledging failures and its effect in 
# "F models" is actually a surrogate effect from "urban_intensity". So I'll only diagnose the "H 
# models".
# Similarly, the surprising effects of the temperature proxies might actually be linked to humidity, a
# variable we could not measure.

ttFS_zibbin_glm2h <- glmmTMB::glmmTMB(fledgling_nb/brood_size ~ c.log_patch_area * 
                                        c.log_F_metric_d2b1 +
                                        clutch_size +
                                        urban_intensity + manag_mid + manag_high +
                                        light_pollution + noise_m + traffic +
                                        min_t_between + laying_day + year,
                                     weights = brood_size, data = ntits3,
                                     family = glmmTMB::betabinomial(link = "logit"),
                                     ziformula = ~min_t_between+urban_intensity+year)
ttFS_zibbin_glmm2h <- glmmTMB::glmmTMB(fledgling_nb/brood_size ~ c.log_patch_area * 
                                         c.log_F_metric_d2b1 +
                                         clutch_size +
                                         urban_intensity + manag_mid + manag_high +
                                         light_pollution + noise_m + traffic +
                                         min_t_between + laying_day + year + (1|id_nestbox),
                                     weights = brood_size, data = ntits3,
                                     family = glmmTMB::betabinomial(link = "logit"),
                                     ziformula = ~min_t_between+urban_intensity+year)
summary(ttFS_zibbin_glm2h) # AIC = 1362 vs 1374.5.
summary(ttFS_zibbin_glmm2h) # AIC = 1364 vs 1376.5.
# Note also that replacing "cumdd_before" by "min_t_before" does not change things much!
```

\
\

******

## 3.2. Conclusion on the exploratory ZI models

As could have been expected, tuning the zero-inflation (ZI) component of the *nestling survival* models (reminder: zero-inflated beta-binomial GLM(M)s) **quite strongly improved** the predictive abilities of the models, as measured by AIC. Among these *exploratory ZI models*, the best ones we could think of were the ones using *min_t_between*, *urban_intensity*, and *years* as predictors of the ZI, which all turned out significant or almost significant with a gain of 10 to 12 points of AIC depending on model considered (i.e. the `ttFS_zibbin_glmm1h` and `ttFS_zibbin_glmm2h` models)!  
Diagnostics for these models were mostly ok: there was no outliers, deviations, dispersion or
distributional problems. Predictions were fairly good as well but the models still made too narrow predictions and failed to correctly predict total successes and failures (so this is quite similar to our final inferential models).  

These exploration thus suggest that increased *urban intensity* and *minimal temperatures* during the rearing of nestlings lowers their chances of survival.  
We also tried removing "traffic" but it didn't change things much. When we used the *F-metric*
along with *urban_intensity* to model the ZI-part of the model, the effect of the former
utterly disappears suggesting that connectivity does not influence total fledging failures and
its effect in "F models" was actually a surrogate effect from "urban_intensity".

